% begin presentation setup
\documentclass{beamer}
%\documentclass[handout,xcolor=pdftex,dvipsnames,table]{beamer}

\usetheme{Ilmenau}
\usefonttheme{structuresmallcapsserif}
\usecolortheme{lily}
% end presentation setup

\title{Gender Differences in Mate Selection: Evidence from a Speed Dating Experiment}
\author{Raymond Fisman, Sheena S. Iyengar, Emir Kamenica, and Itamar Simonson \thanks{Presented by B. Champion, B. Flaxman, and K. McLean}}
\date{\today}

\begin{document}
\maketitle

\begin{frame} \frametitle{Motivation and Question}
    \setbeamercovered{dynamic} \begin{itemize}
        \item Marriage partner selection has profound effect on people and society. \pause
        \item Marriage partner selection doesn't come from the general population, but from a pool of the individual's dating partner choices.
        \item How do cis-het men and women choose partners differently from each other?  \pause
        \item What are the significant factors in those choices?
    \end{itemize}
\end{frame}

\begin{frame} \frametitle{Contribution}
    \setbeamercovered{dynamic} \begin{itemize}
        \item Economics has mostly focused on marriage, only looking at dating recently.\pause
        \item Dating long studied in psychology through surveys, not experiments.
    \end{itemize}
\end{frame}


\begin{frame} \frametitle{Methodology}
    \setbeamercovered{dynamic} \begin{itemize}
        \item 392 graduate and professional students take part in 14 weekday night Speed Dating events from 2002 to 2004 near Columbia University. \pause
        \item The group size is the only variation between events. \pause
        \item Subjects rated every partner on a 10 point scale for Attractive, Sincere, Intelligent, Fun, Ambitious, and Shared Interests as well as indicated whether they would like to meet the partner again. \pause
        \item Subjects also rated themselves in the pre-event survey, as well as provide other biographical data (field of study, ZIP where they grew up, and race).
    \end{itemize}
\end{frame}

\begin{frame} \frametitle{Key Findings I}
    \setbeamercovered{dynamic} \begin{itemize}
        \item No preference differences between cis-het men and women with regards to Sincere, Fun, or Shared Interests. \pause
        \item Cis-het men "put more weight on physical attractiveness than (cis-het women) do, while (cis-het women) put more weight on intelligence."\footnote{p 682}  \pause
        \item Cis-het men "do not value (cis-het) women's intelligence or ambition when it exceeds their own; moreover, a (cis-het) man is less likely to select a (cis-het) woman whom he perceives to be more ambitious than he is." \footnote{p 685}
    \end{itemize}
\end{frame}

\begin{frame} \frametitle{Key Findings II}
    \setbeamercovered{dynamic} \begin{itemize}
        \item Cis-het "women prefer partners from more affluent neighborhoods, and both (cis-het) men and women are more likely to accept a partner who grew up in a less densely populated area."\footnote{p 686} \pause
        \item Cis-het "women exhibit strong preference for partners of their own race, while (cis-het) men do not."\footnote{p 689}
        \item Cis-het women "become significantly more selective in larger groups; (cis-het men) do not."\footnote{p 689}
    \end{itemize}
\end{frame}


\end{document}